% !TeX root=main.tex
% در این فایل، عنوان پایان‌نامه، مشخصات خود و چکیده پایان‌نامه را به انگلیسی، وارد کنید.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\baselineskip=.6cm
\begin{latin}
    \latinuniversity{Iran University of Science and Technology}
    \latinfaculty{Computer Engineering Department}
    \latinsubject{Computer Engineering }
    \latinfield{Software Engineering}
    \latintitle{Code Smell Detection with Suggested Large Language Models}
    \firstlatinsupervisor{Dr. Saeid Parsa}
    %\secondlatinsupervisor{Second Supervisor}
    %\firstlatinadvisor{Dr. Einollah Khanjari}
    \secondlatinadvisor{Dr. X}
    \latinnameF{\lr{Mohammad Sadegh}}
    \latinsurnameF{\lr{Poulaei Moziraji}}
    \latinnameS{\lr{Sayin}}
    \latinsurnameS{\lr{Ala}}
    \latinthesisdate{August 2024}
    \latinkeywords{Code Smells, Large Language Models, Deep Learning, Automatic Detection, Transformer, Model Optimization}
    \en-abstract{This research proposes a model for detecting code smells using large language models. Code smells refer to concepts and features in programming code that may indicate deeper issues in software design and implementation. These issues can lead to reduced code quality and increased complexity in maintenance and development. The proposed method leverages large language models trained on labeled datasets, capable of detecting 28 different types of code smells. The model is developed using advanced deep learning techniques and architectures, such as Transformers. Evaluation results show that the proposed model significantly improves the accuracy of code smell detection and can serve as an effective tool for software developers. The research also addresses the challenges in training and optimizing large language models and provides solutions to enhance the model's performance.}
    \latinfirstPage
\end{latin}
